HBCC - ACC - STG - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-02-19 cmc-rnaseq-de/HBCC_ACC-STG_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
plot tissue correlation

>>>>

### Tissue Correlation
```{r tissue_correlation}
hasReps = COVARIATES %>%
  dplyr::select(Individual_ID) %>% 
  table

df_dlpfc = COVARIATES %>% 
  filter( Individual_ID %in% names(hasReps[hasReps==2])) %>%
  filter(grepl("DLPFC", Dx.Tissue)) %>% 
  dplyr::select(SampleID, Individual_ID, Dx.Tissue)
df_acc = COVARIATES %>%
  filter( Individual_ID %in% names(hasReps[hasReps==2])) %>%
  filter(grepl("ACC", Dx.Tissue)) %>% 
  dplyr::select(SampleID, Individual_ID, Dx.Tissue)

df_merge = merge(df_dlpfc, df_acc, by="Individual_ID")

corRes = sapply(res_std$ensembl_gene_id, function(ensGene){

  x = VOOM.GENE_EXPRESSION$E[ensGene,df_merge$SampleID.x,drop=FALSE]
  y = VOOM.GENE_EXPRESSION$E[ensGene,df_merge$SampleID.y,drop=FALSE]

  cor(t(x)[,1], t(y)[,1], use="pairwise.complete.obs")
})

hist(corRes, xlab="Correlation", main="Correlation between ACC and DLPFC sample from the sample individual for each gene from ")

pca = prcomp(t(VOOM.GENE_EXPRESSION$E))

df_pca = merge(pca$x, as.data.frame(cov_dream), by.x="row.names", by.y="SampleID" )

ggplot(df_pca, aes(PC1, PC2, color=Tissue, shape=Institution)) + geom_point() + theme_bw(17) + theme(aspect.ratio=1)
```
